Arrows for Parallel Computations

### 2017-09-25 paper/content/parallelHaskells.tex
tmp

\subsection{Short introduction to parallel Haskells}
\label{sec:parEvalNIntro}
There are already several ways to write parallel programs in Haskell. As we base our parallel Arrows on existing parallel Haskells, we will now give a short introduction to the ones we use as backends in this paper.

@@

\subsubsection{Multicore Haskell}
Multicore Haskell \cite{Marlow2009,Trinder1998a} is a way to do parallel processing found in standard GHC.\footnote{Multicore Haskell on Hackage is available under \url{https://hackage.haskell.org/package/parallel-3.2.1.0}, compiler support is integrated in the stock GHC.} It ships with parallel evaluation strategies for several types which can be applied with |using :: a -> Strategy a -> a|. Let:

>>>>

\subsection{Short introduction to parallel Haskells}
\label{sec:parEvalNIntro}
There are already several ways to write parallel programs in Haskell:

\begin{table}[]
\centering
\caption{Overview over some parallel Haskells}
\label{my-label}
\begin{tabular}{\pipe l \pipe l \pipe l \pipe} 
Name		& Memory setting & Concepts used \\
GpH         & shared \& distributed & |par|/|pseq| "hints" \\
|Par| Monad & shared & deterministic parallel Monad \\
Eden        & shared \& distributed & special compiler, pure \& monadic interface \\
HdpH        & \mbcomment{shared?} \& distributed & parallel Monad, Template Haskell \\
LVish       & shared & parallel Monad, parallel data-structures\\
\end{tabular}
\end{table}

As we base our parallel Arrows on existing parallel Haskells, we will now give a short introduction to the ones we use as backends in this paper.

@@

\subsubsection{Multicore Haskell}
Multicore Haskell \cite{Marlow2009,Trinder1998a} is one of the simplest ways to do parallel processing found in standard GHC.\footnote{Multicore Haskell on Hackage is available under \url{https://hackage.haskell.org/package/parallel-3.2.1.0}, compiler support is integrated in the stock GHC.} Besides some basic primitives it ships with parallel evaluation strategies for several types which can be applied with |using :: a -> Strategy a -> a|, which is exactly what is required for an implementation of |parEvalN|.
